---
output: github_document
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/jhudsl/leanbuild/workflows/R-CMD-check/badge.svg)](https://github.com/jhudsl/leanbuild/actions)
<!-- badges: end -->

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# leanbuild Package:

The goal of `leanbuild` is to provide tools to convert from Bookdown content to Leanpub content and do some checks.

## Installation

You can install `leanbuild` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("jhudsl/leanbuild")
```


## Example

Within a bookdown repository, you can run the following command to convert your
content to a Leanpub-ready format.

```{r, eval = FALSE}
leanbuild::bookdown_to_leanpub()
```

By default the output files will be sent to a `manuscript` folder which is what Leanpub looks for.

For an example of what this looks like, see [this template repository](https://github.com/jhudsl/OTTR_Quizzes).
